# Mortality rate of children under five

```{r, echo=FALSE, message=FALSE}
library(reshape2)
library(pander)
library(ggplot2)

opts_chunk$set(echo=FALSE)
```

I want to show how easy it is to build dynamic reports using the R package knitr with a Makefile. This document explores child mortality data downloaded from the World Bank.

```{r}
options(stringsAsFactors=FALSE)
wide <- read.csv('data/mortality_rates.csv', skip=2)

indicator.name <- 'Mortality rate, under-5 (per 1,000 live births)'
stopifnot(all(wide$Indicator.Name == indicator.name))
wide$Indicator.Name <- NULL
wide$Indicator.Code <- NULL

for (col in names(wide)) {
    if (all(is.na(wide[[col]]))) {
        wide[[col]] <- NULL
    }
}

long <- melt(wide, id.vars=c('Country.Name', 'Country.Code'))
long$year <- as.integer(substr(as.character(long$variable), 2, 5))
long$variable <- NULL

names(long)[names(long) == 'value'] <- 'mortality.under.five'
```

Below are some summary statistics of the numeric variables in the dataset.

```{r, results='asis'}
MyStats <- function(x) c(
    Min=min(x, na.rm=TRUE),
    Mean=mean(x, na.rm=TRUE),
    Max=max(x, na.rm=TRUE),
    Missing=sum(is.na(x)) / length(x)
    )
numeric.columns <- sapply(long, is.numeric)
summary.stats <- t(sapply(long[numeric.columns], MyStats))
pandoc.table(summary.stats, style='rmarkdown', caption='Summary statistics')
```

This report expects a single parameter to be passed in, a country code. With that country code we creat a graph comparing the change in child mortality over time for that country to all other countries in the world.

```{r, fig.width=10}
long$in.country <- long$Country.Code == country.code
country.name <- unique(long$Country.Name[long$in.country])

keep <- !is.na(long$mortality.under.five)
g <- (
    ggplot(long[keep, ], aes(x=year, y=mortality.under.five, group=Country.Code, color=in.country, size=in.country)) +
    geom_line(alpha=0.25) +
    theme_bw() +
    theme(legend.title=element_blank()) +
    scale_color_manual(values=c('black', 'red'),
                       labels=c('Rest of the world', country.name)) + 
    scale_size_manual(values=c(0.5, 3),
                      labels=c('Rest of the world', country.name)) +
    ylab('Mortality rate of children under five') +
    xlab('Year') +
    ggtitle('Mortality rate of children under five over time by country')
    )
print(g)
```

We can embed variable contents inline! This report focuses on `r country.name`. I think this will be a very nice tool for Dimagi.
