# `r rendering__name`
Based on data collected using `r form__name`.

```{r, echo=FALSE}
library(ggplot2)
library(pander)

pie_chart <- function(data, x, y, title) {
  data[['label']] <- paste0(data[[x]], ' = ', round(data[[y]]), '%')
  data[['empty']] <- factor(0)
  
  pie <- (
    ggplot(data, aes_string(x='empty', y=y, fill='label')) +
    geom_bar(stat='identity', width = 1) +
    labs(title=title, x='', y='') + 
    theme_bw() +
    theme(
      axis.ticks.y=element_blank(),
      axis.text.y=element_blank(),
      axis.text.x=element_blank(),
      panel.grid.major.y=element_blank(),
      panel.border=element_blank()
    ) +
    coord_polar(theta='y') +
    guides(fill=guide_legend(title=''))
  )
  
  return(pie)  
}

respondents <- data

if ("UrbanM4M" %in% names(respondents)) {
  urbanrespondents <- respondents[respondents$UrbanM4M == 1,]
  urbanmessage <- paste(nrow(urbanrespondents), " respondents were urban residents.")
  if(nrow(urbanrespondents)) {
    show_urban <- TRUE
  } else {
    show_urban <- FALSE
  }
    
} else {
  urbanrespondents <- respondents
  urbanmessage <- "Note that all respondents were assumed to be urban residents."
  show_urban <- TRUE
}

if (!as.logical(request__show_urban)) {
  show_urban <- FALSE
}


cutoff <- 100
n <- nrow(respondents)
warning_message <- n < cutoff

density <- data.frame(Quintile=1:5)
density$Percentage <- sapply(density$Quintile, function(i) {
    100 * sum(respondents$NationalQuintile == i) / nrow(respondents)
})

my_table <- data.frame(
  k=c(as.character(density$Quintile), 'Total'),
  v=c(density$Percentage, sum(density$Percentage))
  )
names(my_table) <- c('Wealth quintile', 'Percentage of respondents')

bottom_two <- sum(density$Percentage[density$Quintile %in% c(1, 2)])
```

`r n` respondents have been interviewed.

```{r, echo=FALSE, results='asis'}
if (warning_message) {
    cat(paste(
        'We encourage you to consider your sample size when interpreting results. This sample of',
        n,
        'may be small.'
        ))
}
```

## National quintile results

<div style="float: left;">
```{r, echo=FALSE, fig.width=4, fig.height=3}
pie_chart(density, x='Quintile', y='Percentage', title='')
```

```{r, echo=FALSE, results='asis'}
pandoc.table(my_table, style='rmarkdown', round=1, keep.trailing.zeros=TRUE, justify='left')
```
</div>

These are the national quintile results for these respondents. These results indicate how your respondents compare to the national population.

The table shows you the percentage of your respondents that were
in each national wealth quintile.  Quintile 1 is the lowest wealth quintile and quintile 5 is the highest wealth quintile.

`r round(bottom_two)`% of your respondents were in the bottom two
quintiles. This means that a relatively `r ifelse(bottom_two >= 40,
'large', 'small')` number of respondents were poor. For more
information on interpreting wealth quintile results,
[please click here](http://www.equitytool.org/wealth-quintiles/).


<div style="clear: both;"></div>


`r if (show_urban) '## Urban quintile results'`

<div style="float: left;">
```{r, echo=FALSE, fig.width=4, fig.height=3}
density <- data.frame(Quintile=1:5)
density$Percentage <- sapply(density$Quintile, function(i) {
    100 * sum(urbanrespondents$UrbanQuintile == i) / nrow(urbanrespondents)
})

my_table <- data.frame(
  k=c(as.character(density$Quintile), 'Total'),
  v=c(density$Percentage, sum(density$Percentage))
  )
names(my_table) <- c('Wealth quintile', 'Percentage of respondents')

bottom_two <- sum(density$Percentage[density$Quintile %in% c(1, 2)])

if (show_urban){
  pie_chart(density, x='Quintile', y='Percentage', title='')
}
```

```{r, echo=FALSE, results='asis'}
if (show_urban){
  pandoc.table(my_table, style='rmarkdown', round=1, keep.trailing.zeros=TRUE, justify='left')
}
```
</div>

`r paste(urbanmessage)`
`r if (show_urban) 'These are the urban quintile results for these respondents. These are the results comparing your respondents to urban residents only. 

The table shows you the percentage of your respondents that were
in each urban wealth quintile. Quintile 1 is the lowest wealth quintile and quintile 5 is the highest wealth quintile.'`

`r if (show_urban) round(bottom_two)`
`r if (show_urban) '% of your respondents were in the bottom two
quintiles. This means that a relatively '`
`r if (show_urban) ifelse(bottom_two >= 40,
'large', 'small')` 
`r if (show_urban) 'number of respondents were poor. For more
information on interpreting wealth quintile results,
[please click here](http://www.equitytool.org/wealth-quintiles/).'`


<div style="clear: both;margin-bottom:120px;"></div>
