# Wealth Quintile Results

```{r, echo=FALSE}
cutoff <- 50
n <- nrow(data)
warning_message <- n < cutoff
report <- !warning_message
```

`r n` respondents have been interviewed.

{{#warning_message}}
Warning: Your sample is too small. Collect at least `r cutoff` responses to be representative.
{{/warning_message}}

{{#report}}
## National quintile results

These are the national quintile results for these respondents: 

```{r, echo=FALSE}
library(ggplot2)

density <- as.data.frame(table(data$Quintile) / nrow(data) * 100)
names(density) <- c('Quintile', 'Percentage')
density$label <- paste0(round(density$Percentage, 1), '%')
(
  ggplot(density, aes(x=Quintile, y=Percentage, fill=Quintile)) + 
  geom_bar(stat='identity') + 
  ggtitle('Respondents by wealth quintile') + 
  ylab('Percentage of respondents') + 
  xlab('Wealth quintile') + 
  geom_text(aes(y=Percentage+0.75, label=label, color=Quintile)) + 
  guides(fill=FALSE, color=FALSE)
)

bottom_two <- sum(density$Percentage[density$Quintile %in% c(1, 2)])
```

The graph above shows you the percentage of your respondents that were in each national wealth quintile.

`r round(bottom_two)`% of your respondents were in the bottom two quintiles. For more information on interpreting wealth quintile results, [please click here](http://somestaticlink).
{{/report}}