# Project Results

```{r, echo=FALSE}
respondents <- data

cutoff <- 100
n <- nrow(respondents)
warning_message <- n < cutoff
```

`r n` respondents have been interviewed.

{{#warning_message}}
Warning: Your sample is too small. Collect at least `r cutoff` responses to be representative.
{{/warning_message}}

<div style="float: left;">
```{r, echo=FALSE, fig.width=4, fig.height=3}
library(ggplot2)

density <- as.data.frame(table(respondents$NationalQuintile) / nrow(respondents) * 100)
names(density) <- c('Quintile', 'Percentage')

my_table <- data.frame(
  k=c(as.character(density$Quintile), 'Total'),
  v=c(density$Percentage, sum(density$Percentage))
  )
names(my_table) <- c('Wealth quintile', 'Percentage of respondents')

pie_chart <- function(data, varname) {
  var <- factor(data[[varname]])
  percent <- round(100 * table(var) / length(var), 1)
  label <- paste0(var, ' = ', percent[var], '%')
  data[[varname]] <- label
  data[['empty']] <- factor(0)
  
  pie <- (
    ggplot(data, aes_string(x='empty', fill=varname)) +
    geom_bar(width = 1) +
    ylab('') + 
    xlab('') + 
    theme_bw() +
    theme(axis.ticks.y=element_blank(), axis.text.y=element_blank(), panel.grid.major.y=element_blank(), panel.border=element_blank()) +
    coord_polar(theta = "y")
  )
  
  return(pie)  
}

pie_chart(respondents, 'NationalQuintile')

bottom_two <- sum(density$Percentage[density$Quintile %in% c(1, 2)])
```
```{r, echo=FALSE, results='asis'}
library(pander)

pandoc.table(my_table, style='rmarkdown', round=1, keep.trailing.zeros=TRUE, justify='left')
```
</div>

## National quintile results

These are the national quintile results for these respondents.

The table above shows you the percentage of your respondents that were in each national wealth quintile.

`r round(bottom_two)`% of your respondents were in the bottom two quintiles. This means that a relatively `r ifelse(bottom_two >= 40, 'large', 'small')` number of respondents were poor. For more information on interpreting wealth quintile results, [please click here](http://www.equitytool.org/wealth-quintiles/).


<div style="clear: both;margin-bottom:120px;"></div>
